---
title: "765_consuling_project"
output:
  github_document:
  html_document:
    df_print: paged
---

```{r,include=F}
library(tidyverse)
library(data.table)
library(skimr)
library(gtsummary)
library(readxl)
library(sf)
library(mapview)
library(ggmap)
```
# Behavioral Health 911 Call Notes(Draft)

Using detroit_analysis data, we will find out a meaningful observation. The things we will do includes hypothesis test of null no difference of the number of calls based on hour, month, weekday. Also, since we have census track data, we will do spatial analysis to see the feature of location of calls.

## Exploration data Analysis

```{r, echo=F}
data <- read_excel('detroit_analysis.xlsx') %>% as.data.frame()
```

Data consists of 48318 * 23 matrix and there are some NA values in some columns. If I need to adjust NA values, I will mention it if necessary.

## Analyses

### Time series of counts

First of all, we will see the glimpse of difference of the number of calls with several barplots.

```{r, echo= F}
# Let's go with Monthly
data_bar_month <- data %>% 
  group_by(month) %>% 
  summarise(sum = n())

month_name <- c('Jan', 'Feb', 'Mar', 'Apr', "May", 'Jun', 
            'Jul','Aug', 'Sep','Oct','Novr','Dec')

data_bar_month <- cbind(data_bar_month, month_name) %>% as.data.frame()

# This time weekday

data_bar_weekday <- data %>% 
  group_by(day_of_week) %>% 
  summarize(sum = n())

week<- c('Sun','Mon','Tues', 'Wedn', 'Thur','Fri', 'Sat')

data_bar_weekday <- cbind(data_bar_weekday, week) %>% as.data.frame()

# hourly
data_bar_hour <- data %>% 
  group_by(hour) %>% 
  summarize(sum = n())

```


```{r setup, echo =F, out.width = '50%', fig.show = 'hold'}
knitr::opts_chunk$set(echo = TRUE)
 ggplot(data_bar_month, aes(x = factor(month_name),y = sum)) + geom_bar(stat= 'identity', fill = 'green') + labs(title = 'The bar graph of the number of call by monthly') + xlab(label = 'Month') + ylab(label = 'The number')

 ggplot(data_bar_weekday, aes(x = factor(week),y = sum)) + geom_bar(stat= 'identity', fill = 'red') + labs(title = 'The bar graph of the number of call by weekday') + xlab(label = 'Weekday') + ylab(label = 'The number')

 ggplot(data_bar_hour, aes(x = factor(hour),y = sum)) + geom_bar(stat= 'identity', fill = 'Yellow') + labs(title = 'The bar graph of the number of call by hour') + xlab(label = 'Hourly') + ylab(label = 'The number')
```


### Spatial Analysis

Let's see the hit map first to see what area has the most calls.





<!-- ```{r, echo = F} -->
<!-- data_long_lati <- data %>%  -->
<!--   group_by(longitude,latitude) %>%  -->
<!--   summarise(n = n()) -->

<!-- mapviewOptions(maxpoints = 300) # diamonds has some 53000 rows -->

<!-- my_sf <- st_as_sf(data_long_lati, coords = c('longitude', 'latitude')) -->

<!-- my_sf <- st_set_crs(my_sf, 4326) -->

<!-- mapview(my_sf, map.types = mapviewGetOption("basemaps"))@map -->


<!-- ```{r} -->
<!-- ggmap::register_google(key = "AIzaSyDSjw6COMi28nOOPXWdQyu3XCmwY7-CQU4", write = TRUE) -->

<!-- lon_mean <- data_long_lati$longitude %>% mean() -->
<!-- lat_mean <- data_long_lati$latitude %>% mean() -->

<!-- get_googlemap(center = c(lon = lon_mean , lat = lat_mean),zoom = 11, markers =  data_long_lati[,1:2], scale = 2) %>% ggmap() -->

<!-- ?get_googlemap -->

<!-- ``` -->







