---
title: "Stat_consulting"
output: github_document
---

```{r,include=F}
library(tidyverse)
library(data.table)
library(skimr)
library(gtsummary)
library(readxl)
library(sf)
library(mapview)
library(ggmap)
```

# Behavioral Health 911 Call Notes(Draft)

## Instruction

In real-life situations, people call 911 for various reasons, including accidents, violence, or fire emergencies. For our analysis, we will specifically focus on the call type 'Behavioral Health,' which can be categorized into 'Mental Health Crisis,' 'Suicidal Threats or Attempts,' or 'Emotional Distress.' The objective is to understand the characteristics of calls falling under this category.

Firstly, we will concentrate on the distribution of 'Behavioral Health' calls over time, considering factors such as hours, months, and weekdays. This will provide insights into when these calls are more likely to occur.

Secondly, employing spatial analysis, we aim to unveil patterns, trends, and relationships that may not be immediately apparent. This analysis will help in understanding the geographical aspects of 'Behavioral Health' calls, offering a comprehensive view beyond temporal considerations. 


## Exploration data Analysis

```{r, echo=F}
data <- read_excel('detroit_analysis.xlsx') %>% as.data.frame()
```

Data consists of 48318 * 23 matrix and there are some NA values in some columns. If I need to adjust NA values, I will mention it if necessary.

## Analyses

### Time series of counts

First of all, we will see the glimpse of difference of the number of calls with several barplots.

```{r, echo= F}
# Let's go with Monthly
data_bar_month <- data %>% 
  group_by(month) %>% 
  summarise(sum = n())

month_name <- c('Jan', 'Feb', 'Mar', 'Apr', "May", 'Jun', 
            'Jul','Aug', 'Sep','Oct','Novr','Dec')

data_bar_month <- cbind(data_bar_month, month_name) %>% as.data.frame()

# This time weekday

data_bar_weekday <- data %>% 
  group_by(day_of_week) %>% 
  summarize(sum = n())

week<- c('Sun','Mon','Tues', 'Wedn', 'Thur','Fri', 'Sat')

data_bar_weekday <- cbind(data_bar_weekday, week) %>% as.data.frame()

# hourly
data_bar_hour <- data %>% 
  group_by(hour) %>% 
  summarize(sum = n())
```



```{r setup, echo =F, out.width = '50%', fig.show = 'hold'}
knitr::opts_chunk$set(echo = TRUE)
 ggplot(data_bar_month, aes(x = factor(month_name),y = sum)) + geom_bar(stat= 'identity', fill = 'green') + labs(title = 'The bar graph of the number of call by monthly') + xlab(label = 'Month') + ylab(label = 'The number')

 ggplot(data_bar_weekday, aes(x = factor(week),y = sum)) + geom_bar(stat= 'identity', fill = 'red') + labs(title = 'The bar graph of the number of call by weekday') + xlab(label = 'Weekday') + ylab(label = 'The number')

 ggplot(data_bar_hour, aes(x = factor(hour),y = sum)) + geom_bar(stat= 'identity', fill = 'Yellow') + labs(title = 'The bar graph of the number of call by hour') + xlab(label = 'Hourly') + ylab(label = 'The number')
```

Based on the plots, we can see there are some difference of frequencies between each months, hours, and weekday. To see it is a statistically significant difference, I would like to use Chisq.test.

```{r, echo= F}
month_prop <- rep(1/12,12)
hour_prop <- rep(1/dim(data_bar_hour)[1],dim(data_bar_hour)[1])
weekday_prop <- rep(1/dim(data_bar_weekday)[1],dim(data_bar_weekday)[1])
```


```{r}
# chisq.test for month
chisq.test(data_bar_month$sum , p = month_prop )
```
```{r}
# chisq.test for month
chisq.test(data_bar_weekday$sum , p = weekday_prop )
```
```{r}
# chisq.test for month
chisq.test(data_bar_hour$sum , p = hour_prop )
```



### Spatial Analysis

Let's see the hit map first to see what area has the most calls.


```{r include=F, eval = F}
data_long_lati <- data %>%
  group_by(longitude,latitude) %>%
  summarise(n = n())

mapviewOptions(maxpoints = 300) # diamonds has some 53000 rows

my_sf <- st_as_sf(data_long_lati, coords = c('longitude', 'latitude'))

my_sf <- st_set_crs(my_sf, 4326)

mapview(my_sf, map.types = mapviewGetOption("basemaps"))@map
```







